Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-18 p2/rec-complete.tex
Clarify the completeness theorem

The reconciliation algorithm defined above is also maximal, that is,
it is not possible to apply any further commands from $A\setminus B$ to $\FS_B$.
To show this, we are going to prove the following theorem:

\begin{myth}\mlabel{rec_is_complete}
If $A$ and $B$ are simple sequences,
and we select a sequence $S\subset \amb$ so that
it contains a command $\cxynv$ for which $\cxynv\nindep\bma$,
then $B\cc S$ either breaks all filesystems $A$ and $B$ do not break
(that is, $S$ breaks all possible $\FS_B$ replicas),
or it changes a node that $B$ has already changed to a different value,
that is, it overrides a change in $\FS_B$.
\end{myth}
Such an override could occur if a given node was modified differently in
$A$ and $B$ (to different values but the same type), which is clearly
a conflict that should be marked for review
by a human or a different system.
\begin{proof}
The proof is similar to the ones we have seen above.
Without loss of generality, we assume that $\cxynv$ is the first command in $S$
that is not independent of $\bmanp$.
If so, we can split $S$ into $S_0\cc\cxynv\cc S_1$ where $S_0\indep\bma$.
Let us also split $\bmanp$ into $T_0\cc\czwmv\cc T_1$ where $T_1\indep\cxynv$.
From \cref{can_move_intersection} we know that
$B\cc S \equiv \acb\cc\bma\cc S$.
We also know that commands in $S_0$ and $\bmanp$ commute, and so this is equivalent to
$\acb\cc S_0\cc\bma\cc\cxynv\cc S_1$.
Expanding $\bmanp$ and swapping $T_1$ and $\cxynv$ we get
\[ \acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv\cc T_1\cc S_1. \]

First, we prove that this sequence breaks all filesystems
unless $n=m$.
Let us therefore suppose $n\neq m$ and, to use an inverse proof,
that the sequence is defined on $\FS$ where $A\aFS\neq\fsbroken$.
If so, its initial segment, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also be defined.

We know $\cxynv\nindep\czwmv$, and so from \cref{incomparable_is_independent}, $n\nunrel m$.
As the sequence is defined, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
As $\czwmv$ and $T_0$ originate from $\bmanp$ and $B$ is simple, we also know there are
no commands on $m$ in $\acbnp$ or $T_0$,
and that there are no commands on $m$ in $S_0$ as $S_0\indep\bma$.

On the one hand we therefore know that $\FS(m)$ must be of type $[z]$,
but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
we also know that $\cxynv$ cannot be applied to $\FS$ without
changing $\FS(m)$ first.
As $A\aFS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
Let this command be $\cqrmv$.

>>>>

The reconciliation algorithm defined above is also maximal, that is,
it is not possible to apply any further commands from $\ambnp$ to $\FS_B$.
To show this, we are going to prove that any sequence $S$ formed from commands
in $\ambnp$ that is not independent of $\bmanp$ necessarily breaks $B\aFS=\FS_B$
or introduces a conflicting update.

\begin{myth}\mlabel{rec_is_complete}
If $A$ and $B$ are simple sequences,
$S'\in\orderset{\ambnp}$,
and $S$ is a subsequence of $S'$ that
contains a command $\cxynv$ for which $\cxynv\nindep\bmanp$,
then $B\cc S$ either breaks all filesystems $A$ and $B$ are defined on
(that is, $S$ breaks all possible $\FS_B$ replicas),
or $S$ changes a node that $B$ has already changed to a different value,
that is, it overrides a change in $\FS_B$.
\end{myth}
Such an override could occur if a given node was modified differently in
$A$ and $B$ (to different values but to values of the same type), which 
our algorithm must treat as a conflict to be resolved by
by the user or a different system.
\begin{proof}
The proof is similar to the ones we have seen above.
Let $T$ be an arbitrary sequence in $\orderset{\bmanp}$.
Without loss of generality, we assume that $\cxynv$ is the first command in $S$
that is not independent of $T$.
If so, we can split $S$ into $S_0\cc\cxynv\cc S_1$ where $S_0\indep T$.

Let $\czwmv$ be the last command in $T$ that is not independent of $\cxynv$,
and split $T$ into $T_0\cc\czwmv\cc T_1$, where therefore $T_1\indep\cxynv$.

From \cref{can_move_intersection} we know that
$\acb\cc\bma \in \orderset{B}$, and so
$B\cc S \equiv \acb\cc\bma\cc S \equiv \acb\cc T\cc S$.
We also know that commands in $S_0$ and $T$ commute, and so this is equivalent to
$\acb\cc S_0\cc T\cc\cxynv\cc S_1$.
Expanding $T$ and swapping $T_1$ and $\cxynv$ we get
\[ \acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv\cc T_1\cc S_1. \]

First, we prove that this sequence breaks all filesystems
where $A$ and $B$ are defined unless $n=m$.
Let us therefore suppose $n\neq m$ and, to use an inverse proof,
that the sequence is defined on $\FS$ where $A\aFS\neq\fsbroken$.
If so, its initial segment, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also be defined.

We know $\cxynv\nindep\czwmv$, and so from \cref{incomparable_is_independent}, $n\nunrel m$.
As the sequence is defined on $\FS$, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
Also, because $B$ is simple and contains $\czwmv$,
we know there are no commands on $m$ 
in either $\acb$ or $T_0$, which are both formed from other commands in $B$.
Moreover, we know there are no commands on $m$ in $S_0$ because $S_0\indep T$.

TODO TODO TODO

On the one hand, we therefore know that $\FS(m)$ must be of type $[z]$,
but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
we also know that $\cxynv$ cannot be applied to $\FS$ without
changing $\FS(m)$ first.
As $A\aFS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
Let this command be $\cqrmv$.
